Architectures and Open pNets

### 2018-02-11 2018-Arch-pNets/arch-pNets.tex
A little bit of uniformisation + comments to Ludo's notes

\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{#2}\Simon}}
\newcommand{\noteSBin}[2][inline,color=green!40]{\todo[#1]{{#2}\Simon}}
\newcommand{\todoSB}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Simon:} {#2}}}
\newcommand{\todoSBin}[2][inline,color=green!40]{\todo[#1]{\textbf{To-do Simon: } {#2}}}
\newcommand{\Ludo}{\\\hfill\mdash Ludo}
\newcommand{\noteLH}[2][color=green!40, size=\tiny]{\todo[#1]{{#2}\Ludo}}
\newcommand{\noteLHin}[2][inline,color=green!40]{\todo[#1]{{#2}\Ludo}}
\newcommand{\todoLH}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Ludo:} {#2}}}
\newcommand{\todoLHin}[2][inline,color=green!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}

@@

@@

\paragraph{Unifying notations -- remarks}

In Archi we have a whereas in pnets we have $\alpha$ where, approximately $\alpha = 
a(x_1..x_n)$ except that a is port name in archi and action name in pnets.
Is this true? can we unify better? or is it sufficient?

states looks ok, but initial state is $s_0$ in pnet and not in archi : $s^0$ . exponent 
position was removed from pnet because we found it complex with indexed set notation but 
could be ok.

@@

  The \emph{composition of $\cB$ with the interaction model
    $\Gamma$} is the component
  $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$,
  where
%
  $Q = \prod_{i \in I} Q_i$;
%
  $q^0 = (q_i^0)^{i \in I}$;
%
  $\val{0}{}: V \rightarrow \data$ is such that, for any $v \in
  V_i$, $\val{0}{}(v) = \val{0}{i}(v)$;
%
  $\export : P \rightarrow 2^V$ is such that, for any $p \in
  P_i$, $\export(p) = \export[i](p)$;
%
  and $\goesto{}$ is the minimal transition relation satisfying
  the rule
%
  \begin{gather}
%%     \label{eq:im:empty}
%%     \infer{
%%       q_j \goesto{\emptyset, g, e} q_j'
%%       \and
%%       \forall i \neq j, q_i = q_i'
%%     }{
%%       (q_i)^{i \in I} \goesto{\emptyset, g, e} (q_i')^{i \in I}
%%     }\,,
%% %
%%     \\[0.5\baselineskip]
    \label{eq:im:int}
%
    \infer{    
      (a, g, e) \in \Gamma
      \and
      a \neq \emptyset
      \and
      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, e_i} q_i'
      \and
      \forall i \not\in \supp{a}, q_i = q_i'
%
      \\\\
      \textstyle
%
      G = g \land \bigwedge_{i \in \supp{a}} g_i
      \and
      E = e; (e_i)^{i \in \supp{a}}
    }{
      (q_i)^{i \in I} \goesto{a, G, E} (q_i')^{i \in I}
    }\,.
  \end{gather}
\end{definition}

@@

\begin{definition}[Safety properties]
  \label{defn:property}
  Let $B$ be a component.  A \emph{safety property} (below,
  simply \emph{property}) of $B$ is a state predicate $\Phi:
  S_{\semopen{B}} \rightarrow \sB$, such that $\bigl((q,
  \val{}{}) \models \Phi\bigr) \land (\val[\primeit]{}{} \order
  \val{}{})$ implies $(q, \val[\primeit]{}{}) \models \Phi$,
  where we write $(q, \val{}{}) \models \Phi$ iff $\Phi(q,
  \val{}{}) = \true$.  A property $\Phi$ is \emph{initial} if
  $s^0_{\semopen{B}} \models \Phi$\todoSB{Do we need this?}\hl{;
    it is \emph{reachable} iff there exists a possibly empty path
    $s^0_{\semopen{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
      \val{2}{}} \cdots \goesto{a^n, \val{n}{}} s^n$, such that
    $s^n \models \Phi$}.
\end{definition}

@@

\begin{definition}[Enforcing properties]
  \label{defn:impose}
  Let $A = (\cC, P_A, V_A, \Gamma)$ be an architecture; let $\cB$
  be a set of components and $\Phi$ an initial property of
  their parallel composition $A_{id}(\cB)$ (see
  \prop{arcomp:nice}).  We say that \emph{$A$ enforces $\Phi$ on
    $\cB$} iff, for every state $s = (s_b, s_c)$ reachable in
  $\semopen{A(\cB)}$, with $s_b \in \prod_{B\in \cB}
  S_{\semopen{B}}$ and $s_c \in \prod_{C \in \cC}
  S_{\semopen{C}}$, we have $s_b \models \Phi$.
\end{definition}

@@

  Clearly the state spaces, initial states and interfaces of both
  components coincide.  Thus we only have to prove that so do the
  transition relations.  Let us assume that
  $\cC = (C_i)^{i \in I}$ and $\cB = (B_j)^{j \in J}$.
  We will use $q^i, q^{i\prime}$ to denote the states of
  $C_i$ and $q_j, q_j'$ to denote the states of $B_j$,
  and similarly for the valuations of variables.

  By \defn{comp:semantics}, a transition
%
  \begin{equation}
    \label{eq:lem1:trans:sem}
    (q^i, \val{i}{})^{i \in I} (q_j, \val{}{j})^{j \in J}
    \goesto{a, \val[\tilde]{}{}}
    (q^{i\prime}, \val{i\prime}{})^{i \in I}
    (q_j', \val{\prime}{j})^{j \in J}
  \end{equation}
%  
  is a transition in $\semopen{A(\cB)}$ (\resp
  $\semopen{A'(\cB)}$) iff
%
  \begin{equation}
    \label{eq:lem1:trans}
    (q^i)^{i \in I} (q_j)^{j \in J}
    \goesto{a, G, E}
    (q^{i\prime})^{i \in I} (q_j')^{j \in J}
    \,,
  \end{equation}
%
  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
%
  \begin{mathpar}
    (\val{i}{})^{i \in I} (\val{}{j})^{j \in J}
    \models G
    \,,
    \and
    (\val{i\prime}{})^{i \in I} (\val{\prime}{j})^{j \in J}
    = \val[\tilde]{}{}[E]
    \,,
    \and
    \valdiff{(\val{i}{})^{i \in I} (\val{}{j})^{j \in J}}{
      \val[\tilde]{}{}} \subseteq \export(a)
    \,.   
  \end{mathpar}

  By \defn{im}, \eq{lem1:trans} is a transition in $A(\cB)$
  iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
  where $P = \bigcup_{B \in \cB \cup \cC} P_B$, and
  %
  \begin{enumerate}
  \item for $i \in I$,
    $q^i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q^{i\prime}$
    is a transition in $C_i$, or
    $a \cap P_{C_i} = \emptyset$ and $q^i = q^{i\prime}$,
    $g_{C_i} = \true$ and $e_{C_i} = \noop$\,;
  \item for $j \in J$,
    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
    is a transition in $B_j$, or
    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
    $g_{B_j} = \true$ and $e_{B_j} = \noop$\,;
  \item $G = g \land \bigwedge_{i \in I} g_{C_i} \land
    \bigwedge_{j \in J} g_{B_j}$ and
    $E = e; (e_{C_i})^{i \in I} (e_{B_j})^{j \in J}$.
  \end{enumerate}
  %

  Similarly, \eq{lem1:trans} is a transition in
  $A'(\cB)$ iff $a \neq \emptyset$,
  $(a, g, e) \in \IMextend{\Gamma}{P}$ and
  %
  \begin{enumerate}
  \item \label{only1:coord}
    $(q^i)^{i \in I}
    \goesto{a \cap P_{C'}, g_{C'}, e_{C'}}
    (q^{i\prime})^{i \in I}$ is a transition in $C'$,
    or $a \cap P_{C'} = \emptyset$ and $q^i = q^{i\prime}$,
    for all $i \in [1,m]$,
    $g_{C'} = \true$ and $e_{C'} = \noop$\,;
  \item for $j \in J$,
    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
    is a transition in $B_j$, or
    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
    $g_{B_j} = \true$, and $e_{B_j} = \noop$;
  \item $G = g \land g_{C'} \land
    \bigwedge_{j \in J} g_{B_j}$ and
    $E = e; e_{C'}, (e_{B_j})^{j \in J}$.
%
  \breakenumistart
  Notice that, for any $i \in I$, since
  $P_{C_i} \subseteq P_{C'}$, we have
  $a \cap P_{C_i} = (a \cap P_{C'}) \cap P_{C_i}$.
  Thus, if $a \cap P_{C'} \neq \emptyset$, 
  the transition in condition~\ref{only1:coord} above is
  present in $C'$ iff
  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$ and
  \breakenumiend
% 
  \item for $i \in I$,
    $q^i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q^{i\prime}$
    is a transition in $C_i$, or $a \cap P_{C_i} = \emptyset$
    and $q^i = q^{i\prime}$,
    $g_{C_i} = \true$ and $e_{C_i} = \noop$,
  \item $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
    $e_{C'} = (e_{C_i})^{i \in I}$.
  \end{enumerate}

\begin{lemma}
  \label{lem:onestep}
  Let $\cB$ be a set of components; let $A_i = (\{C_i\}, V_{A_i},
  P_{A_i}, \Gamma_i)$, for $i = 1,2$, be two architectures
  applicable to $\cB$, with one coordinator each, and denote
  $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
  Finally, let
%
  $
  s_1 s_2 s
%
  \goesto{a, \tilde{\val{}{}}}
%
  s_1' s_2' s'
  $,
%
  be a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$, with
  $a \neq \emptyset$, 
  $s, s' \in \prod_{B \in \cB} S_{\semopen{B}}$
  and
  $s_i, s_i' \in S_{\semopen{C_i}}$ ($i=1,2$).
%
  Then, for $i=1,2$, either $a \cap P_i = \emptyset$ and $s_i s=
  s_i' s'$, or there exists a transition
%
  $
  s_i s
%
  \goesto{a \cap P_i, \val[\doubletilde]{}{}}
%
  s_i' s''
  $ 
%
  in $\semopen{A_i(\cB)}$, with
  $\val[\doubletilde]{}{}$ being the restriction of
  $\val[\tilde]{}{}$ to
  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$ and
  $s' \order s''$.
\end{lemma}
%
\begin{proof}
  By \defn{comp:semantics}, every semantic state consists of a
  component state and a valuation of component variables.  Thus,
  we have
%
  \[
  (q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})
%
  \goesto{a, \tilde{\val{}{}}}
%
  (q_1', \val[\primeit]{}{1}, q_2', \val[\primeit]{}{1}, q', \val[\primeit]{}{})
  \,.
  \]
%
  By \eq{comp:semantics} and \eq{im:int}, this implies
  $(q_1, q_2, q) \goesto {a, G, E} (q_1', q_2', q')$, with
%
  $G = g \land g_1 \land g_2 \land g_b$
  and
  $E = e; (e_1, e_2, e_b)$,
  where
%    
  \begin{mathpar}
    g_b = \bigwedge_{B \in \supp{a} \cap \cB} g_B
    \,,
    \and
    e_b = (e_B)^{B \in \supp{a} \cap \cB}
  \end{mathpar}
%
  and such that $(a, g, e) \in \Gamma$ (see
  \eq{arch:composition}) and
%
  \begin{align}
    \label{eq:guard}
    (\val{}{1}, \val{}{2}, \val{}{}) &\models G
    \,,
    \\
    \label{eq:substitution}
    (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
    &= \val[\tilde]{}{}[E]
    \,,
    \\
    \label{eq:transient}
    \valdiff{(\val{}{1}, \val{}{2}, \val{}{})}{\val[\tilde]{}{}}
    &\subseteq \export(a)
    \,.
  \end{align}
%
  If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
  \eq{transient} and \defn{im}, $s_1 = s_1'$ and $s = s'$
  (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
  \in \exprs{V_a}$).  Hereafter, assume $a \cap P_1 \neq
  \emptyset$.

  Repeating the entire argument $k-1$ times, starting with this
  shorter path, we obtain a path
%
  \begin{equation}
    \label{eq:path-in-1}
    s^0_1 s^0
    %
    \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
    %
    s^1_1 s^{1\prime}
    %
    \goesto{a^2 \cap P_1, \val[\doubletilde]{2}{}}
    %
    s^2_1 s^{2\prime}
    %
    \goesto{a^3 \cap P_1, \val[\doubletilde]{3}{}}
    \cdots
    \goesto{a^k \cap P_1, \val[\doubletilde]{k}{}}
    %
    s^k_1 s^{k'}
  \end{equation}
%  
  with $s^i \order s^{i\prime}$, for all $i \in [1,k]$.

@@

\end{itemize}
\end{definition}
\noteLH[]{}is dom and codom clear?
Now we define
pNet nodes, as constructors for hierarchical behavioural structures.
A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
set of Holes, playing the role of process parameters.

@@

>>>>

\newcommand{\noteSB}[2][color=green!40, size=\tiny]{\todo[#1]{{#2}\Simon}}
\newcommand{\noteSBin}[2][inline,color=green!40]{\todo[#1]{{#2}\Simon}}
\newcommand{\todoSB}[2][color=green!40, size=\tiny]{\todo[#1]{\textbf{To-do Simon:} {#2}}}
\newcommand{\todoSBin}[2][inline,color=green!40]{\todo[#1]{\textbf{To-do Simon: } {#2}}}
\newcommand{\Ludo}{\\\hfill\mdash Ludo}
\newcommand{\noteLH}[2][color=blue!40, size=\tiny]{\todo[#1]{{#2}\Ludo}}
\newcommand{\noteLHin}[2][inline,color=blue!40]{\todo[#1]{{#2}\Ludo}}
\newcommand{\todoLH}[2][color=blue!40, size=\tiny]{\todo[#1]{\textbf{To-do Ludo:} {#2}}}
\newcommand{\todoLHin}[2][inline,color=blue!40]{\todo[#1]{\textbf{To-do Ludo: } {#2}}}

\newcommand{\noteIn}[2][inline,color=black!20]{\todo[#1]{{#2}}}

@@

\subsection*{Unifying notations -- remarks}

\noteIn{In Archi we have $a$, whereas in pNets we have $\alpha$, where, approximately $\alpha = 
a(x_1..x_n)$, except that $a$ is port name in archi and action name in pNets.
Is this true? can we unify better? or is it sufficient?
\Ludo

$a$ is a set of ports, but otherwise, yes, this is true.  I think
this is coherent, since, in archi, we have the ``interaction
part'', \ie only ports, plus the data part, \ie variables,
guards, expressions.  In pNets, these are combined.  So, it seems
ok that notations differ\mdash ``uniformisation'' will be
achieved by encoding archi $\rightarrow$ pNets.  \Simon }

\noteIn{states looks ok, but initial state is $s_0$ in pNet and not in archi : $s^0$.  Exponent 
position was removed from pNet because we found it complex with indexed set notation but 
could be ok.
\Ludo

I am using exponent notation for ``modifiers'', reserving\mdash
as much as possible\mdash index notation for enumeration.  I
think this can be solved, where necessary, by using parentheses,
\eg $(s^0_i)^{i \in I}$
\Simon
}

@@

@@

  The \emph{composition of $\cB$ with the interaction model
    $\Gamma$} is the component
  $\Gamma(\cB) = (Q, q^0, V, \val{0}{}, P, \export, \goesto{})$,
  where
%
  $Q = \prod_{i \in I} Q_i$;
%
  $q^0 = (q_i^0)^{i \in I}$;
%
  $\val{0}{}: V \rightarrow \data$ is such that, for any $v \in
  V_i$, $\val{0}{}(v) = \val{0}{i}(v)$;
%
  $\export : P \rightarrow 2^V$ is such that, for any $p \in
  P_i$, $\export(p) = \export[i](p)$;
%
  and $\goesto{}$ is the minimal transition relation satisfying
  the rule
%
  \begin{gather}
%%     \label{eq:im:empty}
%%     \infer{
%%       q_j \goesto{\emptyset, g, e} q_j'
%%       \and
%%       \forall i \neq j, q_i = q_i'
%%     }{
%%       (q_i)^{i \in I} \goesto{\emptyset, g, e} (q_i')^{i \in I}
%%     }\,,
%% %
%%     \\[0.5\baselineskip]
    \label{eq:im:int}
%
    \infer{    
      (a, g, e) \in \Gamma
      \and
      a \neq \emptyset
      \and
      \forall i \in \supp{a}, q_i \goesto{a \cap P_i, g_i, e_i} q_i'
      \and
      \forall i \not\in \supp{a}, q_i = q_i'
%
      \\\\
      \textstyle
%
      G = g \land \bigwedge_{i \in \supp{a}} g_i
      \and
      E = e; e_i^{i \in \supp{a}}
    }{
      (q_i)^{i \in I} \goesto{a, G, E} (q_i')^{i \in I}
    }\,.
  \end{gather}
\end{definition}

@@

\begin{definition}[Safety properties]
  \label{defn:property}
  Let $B$ be a component.  A \emph{safety property} (below,
  simply \emph{property}) of $B$ is a state predicate $\Phi:
  S_{\semopen{B}} \rightarrow \sB$, such that $\bigl((q,
  \val{}{}) \models \Phi\bigr) \land (\val[\primeit]{}{} \order
  \val{}{})$ implies $(q, \val[\primeit]{}{}) \models \Phi$,
  where we write $(q, \val{}{}) \models \Phi$ iff $\Phi(q,
  \val{}{}) = \true$.  A property $\Phi$ is \emph{initial} if
  $s^0_{\semopen{B}} \models \Phi$.
  %% \todoSB{Do we need this?}\hl{;
  %% it is \emph{reachable} iff there exists a possibly empty path
  %% $s^0_{\semopen{B}} \goesto{a^1, \val{1}{}} s^1 \goesto{a^2,
  %%   \val{2}{}} \cdots \goesto{a^n, \val{n}{}} s^n$, such that
  %% $s^n \models \Phi$}.
\end{definition}

@@

\begin{definition}[Enforcing properties]
  \label{defn:impose}
  Let $A = (\cC, P_A, V_A, \Gamma)$ be an architecture; let $\cB$
  be a set of components and $\Phi$ an initial property of
  their parallel composition $A_{id}(\cB)$ (see
  \prop{arcomp:nice}).  We say that \emph{$A$ enforces $\Phi$ on
    $\cB$} iff, for every state $s = (s_c, s_b)$ reachable in
  $\semopen{A(\cB)}$, with 
  $s_c \in \prod_{C \in \cC} S_{\semopen{C}}$ and
  $s_b \in \prod_{B \in \cB} S_{\semopen{B}}$,
  we have $s_b \models \Phi$.
\end{definition}

@@

@@

\end{itemize}
\end{definition}
\noteLH{is dom and codom clear?}
Now we define
pNet nodes, as constructors for hierarchical behavioural structures.
A pNet has a set of sub-pNets that can be either pNets or pLTSs, and a
set of Holes, playing the role of process parameters.

@@

%****************************************************************
%****************************************************************
\appendix
\clearpage

\section{Proofs}

  Clearly the state spaces, initial states and interfaces of both
  components coincide.  Thus we only have to prove that so do the
  transition relations.  Let us assume that
  $\cC = C_i^{i \in I}$ and $\cB = B_j^{j \in J}$.
  We will use $q_i, q_i'$ to denote the states of
  $C_i$ and $q_j, q_j'$ to denote the states of $B_j$,
  and similarly for the valuations of variables.

  By \defn{comp:semantics}, a transition
%
  \begin{equation}
    \label{eq:lem1:trans:sem}
    (q_i, \val{}{i})^{i \in I} (q_j, \val{}{j})^{j \in J}
    \goesto{a, \val[\tilde]{}{}}
    (q_i', \val{\prime}{i})^{i \in I}
    (q_j', \val{\prime}{j})^{j \in J}
  \end{equation}
%  
  is a transition in $\semopen{A(\cB)}$ (\resp
  $\semopen{A'(\cB)}$) iff
%
  \begin{equation}
    \label{eq:lem1:trans}
    q_i^{i \in I} q_j^{j \in J}
    \goesto{a, G, E}
    (q_i')^{i \in I} (q_j')^{j \in J}
    \,,
  \end{equation}
%
  is a transition in $A(\cB)$ (\resp $A'(\cB)$) and
%
  \begin{mathpar}
    \val{}{i}^{i \in I} \val{}{j}^{j \in J}
    \models G
    \,,
    \and
    (\val{\prime}{i})^{i \in I} (\val{\prime}{j})^{j \in J}
    = \val[\tilde]{}{}[E]
    \,,
    \and
    \valdiff{\val{}{i}^{i \in I} \val{}{j}^{j \in J}}{
      \val[\tilde]{}{}} \subseteq \export(a)
    \,.   
  \end{mathpar}

  By \defn{im}, \eq{lem1:trans} is a transition in $A(\cB)$
  iff $a \neq \emptyset$, $(a, g, e) \in \IMextend{\Gamma}{P}$,
  where $P = \bigcup_{B \in \cB \cup \cC} P_B$, and
  %
  \begin{enumerate}
  \item for $i \in I$,
    $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
    is a transition in $C_i$, or
    $a \cap P_{C_i} = \emptyset$ and $q_i = q_i'$,
    $g_{C_i} = \true$ and $e_{C_i} = \noop$\,;
  \item for $j \in J$,
    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
    is a transition in $B_j$, or
    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
    $g_{B_j} = \true$ and $e_{B_j} = \noop$\,;
  \item $G = g \land \bigwedge_{i \in I} g_{C_i} \land
    \bigwedge_{j \in J} g_{B_j}$ and
    $E = e; e_{C_i}^{i \in I}, e_{B_j}^{j \in J}$.
  \end{enumerate}
  %

  Similarly, \eq{lem1:trans} is a transition in
  $A'(\cB)$ iff $a \neq \emptyset$,
  $(a, g, e) \in \IMextend{\Gamma}{P}$ and
  %
  \begin{enumerate}
  \item \label{only1:coord}
    $(q_i)^{i \in I}
    \goesto{a \cap P_{C'}, g_{C'}, e_{C'}}
    (q_i')^{i \in I}$ is a transition in $C'$,
    or $a \cap P_{C'} = \emptyset$ and $q_i = q_i'$,
    for all $i \in [1,m]$,
    $g_{C'} = \true$ and $e_{C'} = \noop$\,;
  \item for $j \in J$,
    $q_j \goesto{a \cap P_{B_j}, g_{B_j}, e_{B_j}} q_j'$
    is a transition in $B_j$, or
    $a \cap P_{B_j} = \emptyset$ and $q_j = q_j'$,
    $g_{B_j} = \true$, and $e_{B_j} = \noop$;
  \item $G = g \land g_{C'} \land
    \bigwedge_{j \in J} g_{B_j}$ and
    $E = e; e_{C'}, e_{B_j}^{j \in J}$.
%
  \breakenumistart
  Notice that, for any $i \in I$, since
  $P_{C_i} \subseteq P_{C'}$, we have
  $a \cap P_{C_i} = (a \cap P_{C'}) \cap P_{C_i}$.
  Thus, if $a \cap P_{C'} \neq \emptyset$, 
  the transition in condition~\ref{only1:coord} above is
  present in $C'$ iff
  $(a \cap P_{C'}, \true, \noop) \in \Gamma_\cC$ and
  \breakenumiend
% 
  \item for $i \in I$,
    $q_i \goesto{a \cap P_{C_i}, g_{C_i}, e_{C_i}} q_i'$
    is a transition in $C_i$, or $a \cap P_{C_i} = \emptyset$
    and $q_i = q_i'$,
    $g_{C_i} = \true$ and $e_{C_i} = \noop$,
  \item $g_{C'} = \bigwedge_{i \in I} g_{C_i}$ and
    $e_{C'} = e_{C_i}^{i \in I}$.
  \end{enumerate}

\begin{lemma}
  \label{lem:onestep}
  Let $\cB$ be a set of components; let $A_i = (\{C_i\}, V_{A_i},
  P_{A_i}, \Gamma_i)$, for $i = 1,2$, be two architectures
  applicable to $\cB$, with one coordinator each, and denote
  $P_i = P_{C_i} \cup \bigcup_{B \in \cB} P_B$.
  Finally, let
%
  $
  s_1 s_2 s
%
  \goesto{a, \tilde{\val{}{}}}
%
  s_1' s_2' s'
  $,
%
  be a transition in $\semopen{(A_1 \arcomp A_2)(\cB)}$, with
  $a \neq \emptyset$, 
  $s, s' \in \prod_{B \in \cB} S_{\semopen{B}}$
  and
  $s_i, s_i' \in S_{\semopen{C_i}}$ ($i=1,2$).
%
  Then, for $i=1,2$, either $a \cap P_i = \emptyset$ and $s_i s=
  s_i' s'$, or there exists a transition
%
  $
  s_i s
%
  \goesto{a \cap P_i, \val[\doubletilde]{}{}}
%
  s_i' s''
  $ 
%
  in $\semopen{A_i(\cB)}$, with
  $\val[\doubletilde]{}{}$ being the restriction of
  $\val[\tilde]{}{}$ to
  $V_1 = V_{C_1} \cup \bigcup_{B \in \cB} V_B$ and
  $s' \order s''$.
\end{lemma}
%
\begin{proof}
  By \defn{comp:semantics}, every semantic state consists of a
  component state and a valuation of component variables.  Thus,
  we have
%
  \[
  (q_1, \val{}{1}, q_2, \val{}{2}, q, \val{}{})
%
  \goesto{a, \tilde{\val{}{}}}
%
  (q_1', \val[\primeit]{}{1}, q_2', \val[\primeit]{}{1}, q', \val[\primeit]{}{})
  \,.
  \]
%
  By \eq{comp:semantics} and \eq{im:int}, this implies
  $(q_1, q_2, q) \goesto {a, G, E} (q_1', q_2', q')$, with
%
  $G = g \land g_1 \land g_2 \land g_b$
  and
  $E = e; (e_1, e_2, e_b)$,
  where
%    
  \begin{mathpar}
    g_b = \bigwedge_{B \in \supp{a} \cap \cB} g_B
    \,,
    \and
    e_b = e_B^{B \in \supp{a} \cap \cB}
  \end{mathpar}
%
  and such that $(a, g, e) \in \Gamma$ (see
  \eq{arch:composition}) and
%
  \begin{align}
    \label{eq:guard}
    (\val{}{1}, \val{}{2}, \val{}{}) &\models G
    \,,
    \\
    \label{eq:substitution}
    (\val[\primeit]{}{1}, \val[\primeit]{}{2}, \val[\primeit]{}{})
    &= \val[\tilde]{}{}[E]
    \,,
    \\
    \label{eq:transient}
    \valdiff{(\val{}{1}, \val{}{2}, \val{}{})}{\val[\tilde]{}{}}
    &\subseteq \export(a)
    \,.
  \end{align}
%
  If $a \cap P_1 = \emptyset$, then $\supp{a} = \{C_2\}$ and, by
  \eq{transient} and \defn{im}, $s_1 = s_1'$ and $s = s'$
  (recall, \defn{im}, that, for $(a,g,e) \in \Gamma$, we have $e
  \in \exprs{V_a}$).  Hereafter, assume $a \cap P_1 \neq
  \emptyset$.

  Repeating the entire argument $k-1$ times, starting with this
  shorter path, we obtain a path
%
  \begin{equation}
    \label{eq:path-in-1}
    s^0_1 s^0
    %
    \goesto{a^1 \cap P_1, \val[\doubletilde]{1}{}}
    %
    s^1_1 s^{1\prime}
    %
    \goesto{a^2 \cap P_1, \val[\doubletilde]{2}{}}
    %
    s^2_1 s^{2\prime}
    %
    \goesto{a^3 \cap P_1, \val[\doubletilde]{3}{}}
    \cdots
    \goesto{a^k \cap P_1, \val[\doubletilde]{k}{}}
    %
    s^k_1 s^{k\prime}
  \end{equation}
%  
  with $s^i \order s^{i\prime}$, for all $i \in [1,k]$.
